Is high social class always beneficial for survival? Northern Sweden 1801--2013 (cohort version)

### 2018-02-10 pure3b.Rmd
introduce inverse probabiity weighting

>>>>

## Inverse probability weighting

```{r ipw}
head(vb0)
da <- vb0[vb0$sex == "male" & vb0$period == "1876-1900", c("id", "civst", "hisclass", "enter", "exit", "event")]
gg <- as.numeric(da$hisclass)
lfit1 <- glm(gg == 1 ~ civst, data = da, family = "binomial")
p1 <- predict(lfit1, type = "response")
lfit2 <- glm(gg == 2 ~ civst, data = da, family = "binomial")
p2 <- predict(lfit2, type = "response")
lfit3 <- glm(gg == 3 ~ civst, data = da, family = "binomial")
p3 <- predict(lfit3, type = "response")
lfit4 <- glm(gg == 4 ~ civst, data = da, family = "binomial")
p4 <- predict(lfit4, type = "response")
lfit5 <- glm(gg == 5 ~ civst, data = da, family = "binomial")
p5 <- predict(lfit5, type = "response")
tmp <- p1
tmp[gg==2] <- p2[gg==2]
tmp[gg==3] <- p3[gg==3]
tmp[gg==4] <- p4[gg==4]
tmp[gg==5] <- p5[gg==5]
wgt <- 1 / tmp
```
